Appendix0\_10

### 2018-08-20 paper/Appendices/AppendixA.tex
limitation 1
abstract almost done, proof reading first round done

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# NDNS analysis, data management ------------------------------------------}
\CommentTok{# Change the data path accordingly ----------------------------------------}
\KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
\KeywordTok{setwd}\NormalTok{(}\StringTok{"~/Downloads/UKDA-6533-stata11_se/stata11_se/"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(epiDisplay)}
\KeywordTok{library}\NormalTok{(plyr)}
\KeywordTok{library}\NormalTok{(tidyverse)}
\CommentTok{# Read the data into memory -----------------------------------------------}
\KeywordTok{library}\NormalTok{(haven)}
\NormalTok{data <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_foodleveldietarydata_uk.dta"}\NormalTok{)}
\NormalTok{data56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_foodleveldietarydata.dta"}\NormalTok{)}
\NormalTok{data78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_foodleveldietarydata.dta"}\NormalTok{)}
\KeywordTok{names}\NormalTok{(data)}
\KeywordTok{names}\NormalTok{(data56)}
\KeywordTok{names}\NormalTok{(data78)}
\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}

\CommentTok{# Extract the variables needed -------------------------------------------}
\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[,}\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{,}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{5}\NormalTok{,}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{21}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{53}\NormalTok{, }\DecValTok{55}\NormalTok{,}
\DecValTok{57}\NormalTok{,}\DecValTok{58}\NormalTok{,}\DecValTok{59}\NormalTok{,}\DecValTok{60}\NormalTok{,}\DecValTok{61}\NormalTok{,}\DecValTok{62}\NormalTok{,}\DecValTok{63}\NormalTok{,}\DecValTok{64}\NormalTok{,}\DecValTok{65}\NormalTok{)]}
\NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}

@@

\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}

@@

\NormalTok{### Breakfast:       6am to 9am}
\NormalTok{### morning snack:   9am to 12noon}
\NormalTok{### lunch:           12noon to 2pm}
\NormalTok{### afternoon snack: 2pm to 5pm}
\NormalTok{### dinner:          5pm to 8pm}
\NormalTok{### night snack:     8pm to 10pm}
\NormalTok{### midnight:        10pm to 6am}
\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{TimeSlot =} \KeywordTok{cut}\NormalTok{(MealHourN, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{22}\NormalTok{), }
				\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot), }\StringTok{"[22, 6)"}\NormalTok{)}
\NormalTok{Energy}\OperatorTok{$}\NormalTok{TimeSlot[}\KeywordTok{is.na}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)] <-}\StringTok{ "[22, 6)"}
\KeywordTok{tab1}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)}
\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
\CommentTok{# time slot can be calculated --------}
\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
\NormalTok{                          DiaryDaysCompleted, TimeSlot, DayofWeek),  }
\NormalTok{                summarise, }
              \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(Tot_Energ), }
              \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
              \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar),}
              \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Tot_Starch), }
              \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
              \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Tot_Fat), }
              \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
              \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Tot_Alc), }
              \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Tot_NMES))}
\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
\KeywordTok{print}\NormalTok{(new)}
\CommentTok{# Time difference of 3.74195 mins }

\CommentTok{# Calculate the energy from total carbohydrates ---------------------------}
\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.50}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}

\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ] }\CommentTok{# discard those eating occassion }
\CommentTok{# with 0 energy intake }
\KeywordTok{write.csv}\NormalTok{(Energy0, }\DataTypeTok{file =} \StringTok{"Energy_slots.csv"}\NormalTok{) }\CommentTok{# for later analysis}	
\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50%"}\NormalTok{, }\StringTok{">= 50%"}\NormalTok{))}

@@

\NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day2 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day3 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day4 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

@@

\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1 }\OperatorTok{%>%}\StringTok{ }

@@

\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2 }\OperatorTok{%>%}\StringTok{ }

@@

\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3 }\OperatorTok{%>%}\StringTok{ }

@@

\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4 }\OperatorTok{%>%}\StringTok{ }

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# NDNS analysis, data management ------------------------------------------}
\CommentTok{# Change the data path accordingly ----------------------------------------}
\KeywordTok{setwd}\NormalTok{(}\StringTok{".../UKDA-6533-stata11_se/stata11_se/"}\NormalTok{) }
\KeywordTok{library}\NormalTok{(epiDisplay)}
\KeywordTok{library}\NormalTok{(plyr)}
\KeywordTok{library}\NormalTok{(tidyverse)}
\CommentTok{# Read the data into memory -----------------------------------------------}
\KeywordTok{library}\NormalTok{(haven)}
\NormalTok{data <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr1-4a_foodleveldietarydata_uk.dta"}\NormalTok{)}
\NormalTok{data56 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr5-6a_foodleveldietarydata.dta"}\NormalTok{)}
\NormalTok{data78 <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"ndns_rp_yr7-8a_foodleveldietarydata.dta"}\NormalTok{)}
\KeywordTok{names}\NormalTok{(data)}
\KeywordTok{names}\NormalTok{(data56)}
\KeywordTok{names}\NormalTok{(data78)}
\KeywordTok{names}\NormalTok{(data)[}\KeywordTok{names}\NormalTok{(data)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data56)[}\KeywordTok{names}\NormalTok{(data56)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}
\KeywordTok{names}\NormalTok{(data78)[}\KeywordTok{names}\NormalTok{(data78)}\OperatorTok{==}\StringTok{"seriali"}\NormalTok{] <-}\StringTok{ "id"}

\CommentTok{# Extract the variables needed -------------------------------------------}
\NormalTok{df14d <-}\StringTok{ }\NormalTok{data[,}\KeywordTok{c}\NormalTok{(}\DecValTok{113}\NormalTok{,}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{5}\NormalTok{,}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{21}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{53}\NormalTok{, }\DecValTok{55}\NormalTok{,}
\DecValTok{57}\NormalTok{,}\DecValTok{58}\NormalTok{,}\DecValTok{59}\NormalTok{,}\DecValTok{60}\NormalTok{,}\DecValTok{61}\NormalTok{,}\DecValTok{62}\NormalTok{,}\DecValTok{63}\NormalTok{,}\DecValTok{64}\NormalTok{,}\DecValTok{65}\NormalTok{)]}
\NormalTok{var <-}\StringTok{ }\KeywordTok{names}\NormalTok{(df14d)}
\NormalTok{df56d <-}\StringTok{ }\NormalTok{data56 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{df78d <-}\StringTok{ }\NormalTok{data78 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(var)}
\NormalTok{dfs1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(df14d, df56d, df78d)}

@@

\NormalTok{dfs3 <-}\StringTok{ }\NormalTok{dfs3 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id_dy =} \KeywordTok{paste}\NormalTok{(id, DayNo, }\DataTypeTok{sep =} \StringTok{"D"}\NormalTok{))}

@@

\NormalTok{### Breakfast:       6am to 9am}
\NormalTok{### morning snack:   9am to 12noon}
\NormalTok{### lunch:           12noon to 2pm}
\NormalTok{### afternoon snack: 2pm to 5pm}
\NormalTok{### dinner:          5pm to 8pm}
\NormalTok{### night snack:     8pm to 10pm}
\NormalTok{### midnight:        10pm to 6am}
\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{TimeSlot =} \KeywordTok{cut}\NormalTok{(MealHourN, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{22}\NormalTok{), }
				\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}
\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{levels}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot), }\StringTok{"[22, 6)"}\NormalTok{)}
\NormalTok{Energy}\OperatorTok{$}\NormalTok{TimeSlot[}\KeywordTok{is.na}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)] <-}\StringTok{ "[22, 6)"}
\KeywordTok{tab1}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{TimeSlot)}
\CommentTok{# For each subject, the total energy/carbohydrate intake for each }
\CommentTok{# time slot can be calculated --------}
\NormalTok{old<-}\KeywordTok{Sys.time}\NormalTok{()}
\NormalTok{Energy <-}\StringTok{ }\KeywordTok{ddply}\NormalTok{(Energy, .(id_dy, id, SurveyYear, DayNo, Age, Sex, }
\NormalTok{                          DiaryDaysCompleted, TimeSlot, DayofWeek),  }
\NormalTok{                summarise, }
              \DataTypeTok{Tot_Energ =} \KeywordTok{sum}\NormalTok{(Tot_Energ), }
              \DataTypeTok{Tot_Carb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
              \DataTypeTok{Tot_Sugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar),}
              \DataTypeTok{Tot_Starch =} \KeywordTok{sum}\NormalTok{(Tot_Starch), }
              \DataTypeTok{Tot_Fibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
              \DataTypeTok{Tot_Fat   =} \KeywordTok{sum}\NormalTok{(Tot_Fat), }
              \DataTypeTok{Tot_Prot  =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
              \DataTypeTok{Tot_Alc   =} \KeywordTok{sum}\NormalTok{(Tot_Alc), }
              \DataTypeTok{Tot_NMES  =} \KeywordTok{sum}\NormalTok{(Tot_NMES))}
\NormalTok{new<-}\KeywordTok{Sys.time}\NormalTok{()}\OperatorTok{-}\NormalTok{old}
\KeywordTok{print}\NormalTok{(new)}
\CommentTok{# Time difference of 3.74195 mins }

\CommentTok{# Calculate the energy from total carbohydrates ---------------------------}
\NormalTok{Energy <-}\StringTok{ }\NormalTok{Energy }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{KJcarbo =}\NormalTok{ Tot_Carb}\OperatorTok{*}\DecValTok{16}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CarKJpercentage =}\NormalTok{ KJcarbo}\OperatorTok{/}\NormalTok{Tot_Energ) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Carbo =} \KeywordTok{cut}\NormalTok{(CarKJpercentage, }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.50}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{right =} \OtherTok{FALSE}\NormalTok{))}

\NormalTok{Energy0 <-}\StringTok{ }\NormalTok{Energy[}\OperatorTok{!}\NormalTok{(Energy}\OperatorTok{$}\NormalTok{Tot_Energ }\OperatorTok{==}\StringTok{ }\DecValTok{0}\NormalTok{), ] }\CommentTok{# discard those eating occassion }
\CommentTok{# with 0 energy intake }
\KeywordTok{write.csv}\NormalTok{(Energy0, }\DataTypeTok{file =} \StringTok{"Energy_slots.csv"}\NormalTok{) }\CommentTok{# for later analysis}	
\NormalTok{Energy0}\OperatorTok{$}\NormalTok{Carbo <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(Energy0}\OperatorTok{$}\NormalTok{Carbo, }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"< 50\%"}\NormalTok{, }\StringTok{">= 50\%"}\NormalTok{))}

@@

\NormalTok{dta_day1 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day2 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day3 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

\NormalTok{dta_day4 <-}\StringTok{ }\NormalTok{Energy0 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(DayNo }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"id_dy"}\NormalTok{, }\StringTok{"Age"}\NormalTok{, }\StringTok{"Sex"}\NormalTok{, }
\StringTok{"DayofWeek"}\NormalTok{,  }\StringTok{"TimeSlot"}\NormalTok{, }\StringTok{"Carbo"}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{  }
StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{DayofWeek =} \KeywordTok{factor}\NormalTok{(DayofWeek, }
\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }
\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{, }
\StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)))}

@@

\NormalTok{dta_d1_wide <-}\StringTok{ }\NormalTok{dta_day1 }\OperatorTok{\%>\%}\StringTok{ }

@@

\NormalTok{dta_d2_wide <-}\StringTok{ }\NormalTok{dta_day2 }\OperatorTok{\%>\%}\StringTok{ }

@@

\NormalTok{dta_d3_wide <-}\StringTok{ }\NormalTok{dta_day3 }\OperatorTok{\%>\%}\StringTok{ }

@@

\NormalTok{dta_d4_wide <-}\StringTok{ }\NormalTok{dta_day4 }\OperatorTok{\%>\%}\StringTok{ }
